Analysis plan

### 2023-02-09 02. Design/MSG-P2312-Analysis Plan-1-clusters.rmd
Update MSG-P2312-Analysis Plan-1-clusters.rmd

We will use Daily Check-In data obtained from Management Science and
Innovation (MSI), a firm contracted to collect and maintain these data.
We will merge in additional variables from the GSA Roster obtained from
D2D. The GSA roster is updated monthly at the end of each month. 
<!-- [We currently have Nov 2022 and Dec 2022 updates; I will try to track down -->
<!-- past months. Ideally, we will merge in each monthly check-in file with -->
<!-- the preceding month's roster file.] -->

@@

We will approach grouping staff and teams in two ways. First,
rules-based groups will be formed. For these, definitions of different
types of work will be defined. Second, groups will be formed using
k-means clustering. This unsupervised machine learning method produces a
defined number of groups (or clusters) minimizing the distance between
the members.

>>>>

We will use Daily Check-In data obtained from Management Science and
Innovation (MSI), a firm contracted to collect and maintain these data.
We will merge in additional variables from the GSA Roster obtained from
D2D. The GSA roster is updated monthly at the end of each month.

@@

<!-- [I might be more discerning about using "staff" vs. "employees" vs. "teams" vs. "groups" vs. "clusters" -- we are grouping employees into teams, but also categorizing them.]  -->
We will approach grouping staff and teams in two ways. First,
rules-based groups will be formed. For these, definitions of different
types of work will be defined. Second, groups will be formed using
k-means clustering. This unsupervised machine learning method produces a
defined number of groups (or clusters) minimizing the distance between
the members.
